Decades of ``group polarization'' replications may be undermined by high false discovery rates

### 2024-12-08 GroupPolarizationStatmod/paper/ms.tex
starting to finalzie draft

\begin{figure}
  \caption{\textbf{Common components of a group polarization experiment.}
  Participants first give their opinion in response to some prompt (A). Afterwards,
  participants deliberate the topic (B). Participants then give their opinion again
  (C). Opinions are implicitly behavioral choices that are most consistent with some
  complex aggregation of brain states and dynamics, and so are theoretically
  continuous (D).}
  \centering
    \includegraphics[width=0.7\textwidth]{Figures/ModelSketchesA-C.pdf}
    \includegraphics[width=0.65\textwidth]{Figures/ModelSketchesD.pdf}
  \label{fig:ModelSketch}
\end{figure}

@@

@@

@@

\begin{figure}
  \caption{\textbf{Significance value, $d^*$, to limit family-wise error 
  rate of 0.05 for each identified study.} \mt{Does this make sense? Order by the
rankings in fdr\_vs\_experiment plots to better understand/compare.}}
  \centering
    \includegraphics[width=0.55\textwidth]{Figures/sigval_for_low_fwer.pdf}
  \label{fig:sigval_for_low_fwer}
\end{figure}

>>>>

\begin{figure}
  \caption{\textbf{Opinions are implicitly behavioral choices that are most consistent with some
  complex aggregation of brain states and dynamics, and so are theoretically
  continuous (A). Common components of a group polarization experiment.}
  Participants first give their opinion in response to some prompt (B). Afterwards,
  participants deliberate the topic (C). Participants then give their opinion again
  (D). }
  \centering
    \includegraphics[width=0.65\textwidth]{Figures/Model/ModelSketchesA.pdf}
    \includegraphics[width=0.7\textwidth]{Figures/Model/ModelSketchesB-D.pdf}
  \label{fig:ModelSketch}
\end{figure}

@@

An opinion is never measured directly, only behaviors meant to indicate one's opinion.
For example, only the location of a mark that a participant makes is measured, not
the complex neural activity that somehow aggregates and expresses some latent
representation. Because so much neural activity must be integrated to yield an opinion,
it is most reasonable to assume opinions are continuous. We call these 
\textit{latent opinions} because they are unobservable. In contrast, ordinal-valued
\text{observed opinions} are the value participants report before and after group
polarization deliberation.

@@

\begin{figure}

  \caption{\textbf{Family-wise error rates and false discovery rates across studies and experiments for
    low, medium, and high Cohen's $d$ significance.}}
  \label{fig:fwer_fdr_synthesis}

  \centering
  \includegraphics[width=1.1\textwidth]{Figures/Results/fwer_fdr_synthesis.pdf}

\end{figure}

@@

\begin{figure}
  \caption{\textbf{Significance value, $d^*$, to limit family-wise error 
  rate of 0.05 for each identified study.} \mt{Does this make sense? Order by the
rankings in fdr\_vs\_experiment plots to better understand/compare.}}
  \centering
    \includegraphics[width=0.75\textwidth]{Figures/Results/sigval_for_low_fwer.pdf}
  \label{fig:sigval_for_low_fwer}
\end{figure}
